\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-28 paper/ms.tex
Table

\documentclass[article, nojss]{jss}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{microtype}
\usepackage{dsfont}

\newcommand{\dnest}{\pkg{DNest4}}

@@

\pkg{emcee} \citep{emcee}

@@

>>>>

\documentclass[article, nojss]{jss}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{microtype}
\usepackage{dsfont}
\usepackage{pifont}

\newcommand{\xmark}{\ding{55}}%
\newcommand{\cmark}{\ding{51}}%
\newcommand{\dnest}{\pkg{DNest4}}

@@

\pkg{emcee} \citep{emcee} is a popular \proglang{Python} package for MCMC
based on affine-invariant ensemble sampling.

@@

The advantages and disadvantages of these various packages, in the opinion
of the authors, are summarized in Table~\ref{tab:packages}.

%\begin{table}
%
%  \begin{tabular}{cc}
%    Knuth & Lamport
%  \end{tabular}}
%\end{table}

\begin{table}
\begin{center}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Package     &   Easy to     & High   &   Multimodal     & Dependent   &   Phase   &   Computes $Z$?\\
            &   implement & dimensions? & distributions? & distributions? & changes? & \\
& models? & & & & &\\
\hline
\pkg{DNest4}    & \xmark  & \cmark & \cmark & \cmark &\cmark &\cmark\\
\pkg{emcee}    & \cmark  & \xmark & \xmark & \cmark &\xmark &\xmark\\
\pkg{JAGS}    & \cmark  & \cmark & \xmark & \xmark & \xmark &\xmark\\
\pkg{MultiNest}    & \cmark  & \xmark & \cmark & \cmark & \cmark &\cmark\\
\pkg{Stan}    & \cmark  & \cmark & \xmark & \cmark & \xmark &\xmark\\
\hline
\end{tabular}}
\caption{\label{tab:packages}}
\end{center}
\end{table}
